\subsection{Line Types and Markers}
PyTV processes source code line by line.
After leading whitespace is ignored, each line is classified as:
\begin{itemize}
  \item \textbf{Inline Python line}: starts with \texttt{//<magic>} (default \texttt{//!}).
  \item \textbf{Python block line}: after a line starting with \texttt{/*<magic>} (default \texttt{/*!}),
  all following lines are Python until a line whose trimmed text is exactly \texttt{*/}.
  Text on the opener line itself is not emitted as Python code.
  \item \textbf{Verilog line}: any line not matched by the two rules above.
\end{itemize}

A minimal example:
\begin{verbatim}
//! a = 1 + 2
assign wire_`a` = wire_b;
/*!
b = a ** 2
*/
\end{verbatim}

The magic marker is configurable by CLI option \texttt{-m/--magic}.
Leading whitespace before markers is allowed.

\subsection{Backtick Expression Substitution}
In Verilog lines, content inside backticks (\verb|`...`|) is treated as a Python expression
and injected through Python f-string formatting in the generated \texttt{.v.py}.
Matching uses a one-line regex equivalent to \verb|`([^`]+)`|,
so nested/multiline backtick expressions are not supported.
For example:
\begin{verbatim}
//! w = 16
input [`w-1`:0] data_in;
\end{verbatim}
renders as:
\begin{verbatim}
input [15:0] data_in;
\end{verbatim}

PyTV escapes braces and single quotes while constructing the generated Python string,
so literal \verb|{| and \verb|}| in Verilog text are preserved.

\subsection{Indentation and Control Flow}
Since Python controls generation, indentation semantics follow Python execution:
\begin{itemize}
  \item Each input line has trailing whitespace removed.
  \item Tabs are converted to spaces using \texttt{-t/--tab-size} (default 4).
  \item For inline Python lines, the first non-empty inline Python line defines a baseline indentation.
  \item Subsequent inline Python lines must keep this baseline, otherwise conversion fails.
  \item In Python block mode, block contents are emitted as Python code (block delimiters are not emitted).
  \item Verilog lines are transformed into \texttt{print(...)} statements at the current Python indentation depth.
\end{itemize}

Practical consequence:
any Python line ending with \texttt{:} (optionally followed by spaces or a comment)
updates the indentation context for following generated Verilog print statements.

In inline mode, a common way to close a control-flow scope before more Verilog is:
\begin{verbatim}
//! for i in range(4):
foo_`i`
//! # return to baseline indentation
bar
\end{verbatim}

\subsection{User Variables and Preamble}
CLI option \texttt{-v/--var KEY=VAL} injects user variables into generated Python before template processing.
This is useful for build-system controlled feature flags and dimensions.

CLI option \texttt{-p/--preamble FILE} prepends a Python preamble file,
allowing helper functions, imports, and shared constants.

\subsection{Instantiation Blocks}
Instantiation blocks are delimited by \texttt{<INST>} and \texttt{</INST>} inside Python regions.
Their body uses YAML mapping syntax.
The \texttt{<INST>} and \texttt{</INST>} markers must be standalone on their Python lines
(except surrounding whitespace).
A basic example:
\begin{verbatim}
//! <INST>
//! module: test_module
//! name: test_inst_`idx`
//! vparams:
//!   W: 32
//! ports:
//!   clk: clk
//!   rst_n: rst_n
//!   data: data_`idx`
//! </INST>
\end{verbatim}

Field definitions are summarized in Table~\ref{tab:inst-fields}.
\begin{table}[htbp]
\centering
\small
\caption{Fields in an \texttt{<INST>} block.}
\label{tab:inst-fields}
\begin{tabularx}{\linewidth}{@{} l c c X @{}}
\toprule
\textbf{Field} & \textbf{Required} & \textbf{Type} & \textbf{Meaning} \\
\midrule
\texttt{module} & Yes & scalar & Module name printed in Verilog and recorded in \texttt{.inst}. \\
\texttt{name} & Yes & scalar & Instance name printed in Verilog and recorded in \texttt{.inst}. \\
\texttt{vparams} & No & mapping & Verilog parameter map rendered as \texttt{\#(...)} and recorded in \texttt{.inst}. \\
\texttt{ports} & No & mapping & Verilog port map rendered as \texttt{(...)} and recorded in \texttt{.inst}. \\
\texttt{parameters} & No & mapping & Metadata-only field stored in \texttt{.inst}; it is not rendered into Verilog instantiation text. \\
\bottomrule
\end{tabularx}
\normalsize
\end{table}

\subsection{Dynamic Group Expansion in Instantiation}
For \texttt{vparams} and \texttt{ports}, PyTV supports grouped expansion with keys prefixed by \texttt{!}
(for example, \texttt{!auto:}):
\begin{verbatim}
//! dyn_ports = [("a", "sig_a"), ("b", "sig_b")]
//! <INST>
//! module: M
//! name: u0
//! ports:
//!   !auto: dyn_ports
//! </INST>
\end{verbatim}

Here \texttt{dyn\_ports} is a Python list of 2-tuples \texttt{(name, value)}.
At render time, PyTV expands the group into individual Verilog mappings and corresponding \texttt{.inst} entries.
The group key after \texttt{!} should use word characters (\texttt{[A-Za-z0-9\_]}) for predictable parsing.
\texttt{<INST>} blocks cannot be nested.
